Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
plz don't finish my scentence

\SubSection{Test Used for H\textsubscript{Fault}}
The frequency of A, B and C faults found were tabularised against the groups which found them. Any response that was not not applicable (NA) was discarded from the table. An example of this is found in table 3. In order to determine if they do find the same faults, a Chi-Square (CS) test of independence was performed on the tabulated results. The reason the CS was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5. Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows. Fishers test should only be used for 2x2 tables.

@@

The results of the study show some interesting results. The rejection of \textsubscript{0} Eff indicates that there is a difference between the efficiency of the inspection methods. This difference could be down to the

@@

\begin{table}
	\centering
	\begin{tabular}[Ht]{| l | l | l | l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults & Mean & Median & Detection Rate\\
	\hline
	UC & 36 & 40 & 35 & 4.615384615 & 3.5 & 0.12 \\
	\hline
	CL & 31 & 47 & 28 & 5.48 & 5 & 0.14 \\
	\hline
	\end{tabular}
	\caption{Results Summary}
\end{table}

The results of the experiment appear to suggest that a check-list(CL) based review technique is more effective than a use-case(UC) based review technique. Given that the null hypothesis H\textsubscript{Eff} was rejected, it is a fair assumption to make. UC appears to find many more class A faults than CL, however, CL finds more class B faults and UC finds more class C faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. The slight variation in favour of the CL technique is further evidence that CL is more efficient and therefore more effective than UC.

>>>>

\SubSection{Test Used for H\textsubscript{Fault}}
The frequency of A, B and C faults found were tabulated against the inspection groups which found them. Any response that was not not applicable (NA) was discarded from the table. An example of this is found in table 3. In order to determine if they do find the same faults, a Chi-Square (CS) test of independence was performed on the tabulated results. The reason the CS was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5. Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows. Fishers test should only be used for 2x2 tables.

@@

The results of the study show some interesting results. The rejection of \textsubscript{0} Eff indicates that there is a difference between the efficiency of the inspection methods.

@@

When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. This, coupled with the rejection of the H\texsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding. A suggestion for a follow up study would be to determine exactly  and why one inspection process finds them over the other.

\begin{table}
	\centering
	\begin{tabular}[Ht]{| l | l | l | l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults & Mean & Median & Detection Rate\\
	\hline
	UC & 36 & 40 & 35 & 4.61 & 3.5 & 0.12 \\
	\hline
	CL & 31 & 47 & 28 & 5.48 & 5 & 0.14 \\
	\hline
	\end{tabular}
	\caption{Results Summary}
\end{table}

The slight variation in favour of the CL technique is further evidence that CL is more efficient and therefore more effective than UC.
